An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-07-12 EconGrowth.Rnw
Edited to-do list.
Changed vertical dimension of ternary plots to provide equilateral triangle.

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
economic growth \sep energy \sep cobb-douglas \sep CES \sep LINEX
%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)
\end{keyword}

@@

\section*{To-do List}
\begin{itemize}
\item{Heun: Add base fit red dots to all cloud plots.}
      \begin{itemize}
      \item{SF}
      \item{CES}
      \item{CESe}
      \item{LINEX}
      \end{itemize}
\item{Heun: Figure out why CESe for ZA with $x$ fails during resampling.}
\item{Heun: Review all assumptions for CES with energy models. 
There are several assumptions for rho and rho1 for various countries. 
When we are resampling, we probably don't want to specify those values.}
\item{Heun: Investigate possible conflicting use of exergy by Warr and Ayres.}
\item{Heun: Get AIC calculations working again.}
\item{Heun: Fix the energy sankey diagram from the seminar}
\item{Heun: Include adjusted sankey diagram in the seminar}
\item{Heun: Add CES production function fits}
      \begin{itemize}
      \item{Write up the decisions about parameter estimation for the 
            CES production function fits}
      \item{Revisit my assumptions for the CES production function 
            (with energy) for each country.}
      \item{Fix the problems with $\sigma_1$ and $\sigma$ values in 
            the CES parameter tables in the appendix}
      \item{Add CES rows to the AIC table. Code is in the 
            \texttt{createAICTable} function, but it is not yet working. 
            Need to find a way to calculate AIC for the object that is 
            returned from the \texttt{cesEst} function.}
      \end{itemize}
\item{Heun: Fix warnings of the form \texttt{Warning:  step factor 0.000488281 reduced below ’minFactor’ of 0.000976562} in the code that generates the Cobb-Douglas with energy fits.}
\item{de Wit: review, critique, and contextualize.}
\item{\st{Heun: Add option for $m = 1$ in single-factor models.}}
\item{\st{Heun: Re-implement confidence interval calculations to use
resampling methods.}}
      \begin{itemize}
      \item{\st{SF}}
      \item{\st{CD}}
      \item{\st{CDe}}
      \item{\st{CES}}
      \item{\st{CESe}}
      \item{\st{LINEX}}
      \end{itemize}
\item{\st{Heun: Include scatter graphs for model parameters 
estimated by resampling methods.}}
      \begin{itemize}
      \item{\st{SF}}
      \item{\st{CD}}
      \item{\st{CDe}}
      \item{\st{CES}}
      \item{\st{CESe}}
      \item{\st{LINEX}}
      \end{itemize}
\item{\st{Heun: Decide if the single factor models should include constraints
on $\alpha$, $\beta$, and $\gamma$. At present, the single-factor model allows
values outside the ranges $\alpha \in (0,1)$, $\beta \in (0,1)$, and $\gamma \in (0,1)$.}}
\item{\st{Heun: Make smaller scatter plots for resample coefficients for those 
countries where $u$ is involved.}}
\item{\st{Heun: Add a table that shows the fraction of unconverged resample fits
for each model, energy type, and factor.}}
\end{itemize}

@@

<<CD_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas (without energy) resample model parameters.">>=
cdResampleTrianglePlot(energyType=NA)
@

Converting the resample data into 95\% confidence intervls 
provides data for Figure~\ref{fig:CD_Params_Graph}.

@@

<<CDq_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas (with $q$) resample model parameters.">>=
cdResampleTrianglePlot(energyType="Q")
@

@@

<<CDx_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas (with $x$) resample model parameters.">>=
cdResampleTrianglePlot(energyType="X")
@

@@

<<CDu_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=threePanelGraphHeight, fig.cap="Cobb-Douglas (with $u$) resample model parameters.">>=
cdResampleTrianglePlot(energyType="U")
@

>>>>

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
economic growth \sep energy \sep Cobb-Douglas \sep CES \sep LINEX
%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)
\end{keyword}

@@

\section*{To-do List}
\begin{itemize}
\item{Heun: Add base fit red dots to all cloud plots.}
      \begin{itemize}
      \item{SF}
      \item{\st{CD}}
      \item{\st{CDe}}
      \item{CES}
      \item{CESe}
      \item{LINEX}
      \end{itemize}
\item{Heun: Figure out why CESe for ZA with $x$ fails during resampling.}
\item{Heun: Review all assumptions for CES with energy models. 
There are several assumptions for rho and rho1 for various countries. 
When we are resampling, we probably don't want to specify those values.}
\item{Heun: Investigate possible conflicting use of exergy by Warr and Ayres.}
\item{Heun: Fix the energy sankey diagram from the seminar}
\item{Heun: Include adjusted sankey diagram in the seminar}
\item{Heun: Add CES production function fits}
      \begin{itemize}
      \item{Write up the decisions about parameter estimation for the 
            CES production function fits}
      \item{Revisit my assumptions for the CES production function 
            (with energy) for each country.}
      \item{Fix the problems with $\sigma_1$ and $\sigma$ values in 
            the CES parameter tables in the appendix}
      \item{Add CES rows to the AIC table. Code is in the 
            \texttt{createAICTable} function, but it is not yet working. 
            Need to find a way to calculate AIC for the object that is 
            returned from the \texttt{cesEst} function.}
      \end{itemize}
\item{Heun: Fix warnings of the form \texttt{Warning:  step factor 0.000488281 reduced below ’minFactor’ of 0.000976562} in the code that generates the Cobb-Douglas with energy fits.}
\item{de Wit: review, critique, and contextualize.}
\item{\st{Heun: Add option for $m = 1$ in single-factor models.}}
\item{\st{Heun: Re-implement confidence interval calculations to use
resampling methods.}}
      \begin{itemize}
      \item{\st{SF}}
      \item{\st{CD}}
      \item{\st{CDe}}
      \item{\st{CES}}
      \item{\st{CESe}}
      \item{\st{LINEX}}
      \end{itemize}
\item{\st{Heun: Include scatter graphs for model parameters 
estimated by resampling methods.}}
      \begin{itemize}
      \item{\st{SF}}
      \item{\st{CD}}
      \item{\st{CDe}}
      \item{\st{CES}}
      \item{\st{CESe}}
      \item{\st{LINEX}}
      \end{itemize}
\item{\st{Heun: Decide if the single factor models should include constraints
on $\alpha$, $\beta$, and $\gamma$. At present, the single-factor model allows
values outside the ranges $\alpha \in (0,1)$, $\beta \in (0,1)$, and $\gamma \in (0,1)$.}}
\item{\st{Heun: Make smaller scatter plots for resample coefficients for those 
countries where $u$ is involved.}}
\item{\st{Heun: Add a table that shows the fraction of unconverged resample fits
for each model, energy type, and factor.}}
\item{\st{Heun: Get AIC calculations working again.}}
\end{itemize}

@@

<<CD_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="Cobb-Douglas (without energy) resample model parameters.">>=
cdResampleTrianglePlot(energyType=NA)
@

Converting the resample data into 95\% confidence intervals 
provides data for Figure~\ref{fig:CD_Params_Graph}.

@@

<<CDq_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="Cobb-Douglas (with $q$) resample model parameters.">>=
cdResampleTrianglePlot(energyType="Q")
@

@@

<<CDx_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="Cobb-Douglas (with $x$) resample model parameters.">>=
cdResampleTrianglePlot(energyType="X")
@

@@

<<CDu_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=threePanelTernaryGraphHeight, fig.cap="Cobb-Douglas (with $u$) resample model parameters.">>=
cdResampleTrianglePlot(energyType="U")
@
